---
title: Comparison of Web-CDI Data Collected from Amazon Mechanical Turk against Data
  from Aggregated CDI studies
author: ''
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
  html_notebook:
    code_folding: hide
    highlight: tango
    theme: spacelab
    toc: yes
  pdf_document:
    toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```


Load up necessary packages and scripts for accessing both the Wordbank MySQL database and the Web-CDI database.

```{r}
packrat::on()
library(tidyverse)
library(quantregGrowth)
library(wordbankr)
library(langcog)
library(stringr)
library(RPostgreSQL)
library(lubridate)
library(robustbase)
library(feather)
library(forcats)
library(magrittr)
library(zipcode)
library(maps)
library(viridis)
theme_set(theme_mikabr(base_size = 14) + theme(panel.border = element_rect(fill = NA) ))

source("helpers/access-webcdi.R")
source("helpers/predictQR_fixed.R")

refresh_data <- T
mode <- "remote"
filter_studies <- T
study_list <- c("Facebook-2-WG", "Facebook-2-WG2", "Facebook-2-WS")
compare_newest_studies <- T
newest_studies <- "Facebook-2-WG2"
taus <- seq(0.01,0.99, 0.01)
# taus <-  c(0.1, 0.25, 0.5, 0.75, 0.9)
allow_longitudinal <- F

```

```{r}

if (refresh_data) {
  source("helpers/gather_data.R")
  gather_data(taus)
}

source("helpers/modeling_functions.R")

data_list <- c("slim_webcdi_data", "slim_wordbank_data", "prod_data", "prod_preds", "comp_preds")

for (i in data_list) {
  temp <- read_feather(paste0("data/",i,".feather"))
  assign(i, temp)
}

```

Filter Web-CDI data
```{r}

slim_webcdi_data <- slim_webcdi_data %>% filter(
  completed &
  (is.na(english) | english > 0.85) &
  (analysis | is.na(analysis)) &
  birth_weight >= 3.5 &
  ((form == "WG" & (age >= 8 & age <= 18)) | (form == "WS" & (age >= 16 & age <= 30)))
)

if (filter_studies) {
  slim_webcdi_data %<>%
    filter(study_name %in% study_list)
}

a <- list(slim_webcdi_data, slim_wordbank_data)

for (i in 1:length((a))) {
  temp <- a[[i]]
  temp <- temp[,c("source","id","form","study_group","study_name","age","sex","mom_ed","mother_education","production","comprehension","n")]
  a[[i]] <- temp

}

both_data <- bind_rows(a) %>% mutate(no_production = (n-production)) %>% ungroup()
levels(both_data$mom_ed)<-c("Decline to Respond","Below Secondary","Secondary","College and Above")

```


Plot Wordbank data with Web-CDI data (in red) along with the original model lines.

```{r}


combined_comprehension_plot <- ggplot(both_data %>% filter(source == "wordbank"),
       aes(x = age, y = (comprehension/n))) +
  geom_jitter(width = .4, size = 1, alpha = .1) +
  geom_line(data = comp_preds, 
            aes(y = pred, col = percentile, group = percentile))

  if (compare_newest_studies) {
    combined_comprehension_plot <- combined_comprehension_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "#249D00", data=both_data %>% filter(source == "webcdi" & study_group != newest_studies), aes(x = age, y = (comprehension/n))) +
    geom_jitter(width = .6, size = 1, alpha = .6, colour = "red", data=both_data %>% filter(source == "webcdi" & study_group == newest_studies), aes(x = age, y =  (comprehension/n)))
  } else{
    combined_comprehension_plot <- combined_comprehension_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "red", data=both_data %>% filter(source == "webcdi"), aes(x = age, y = (comprehension/n)))
  }
  
  combined_comprehension_plot <- combined_comprehension_plot + scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 18, 2),
                     limits = c(8, 18),
                     name = "Age (months)") +
  ylab("Comprehension Vocabulary\n(proportion of total words)") +
  scale_y_continuous(limits = c(0,1), labels = scales::percent) +
  theme(legend.position = "bottom")

  print(combined_comprehension_plot)


combined_production_plot <- ggplot(both_data %>% filter(source == "wordbank"),
       aes(x = age, y = (production/n))) +
  geom_jitter(width = .4, size = 1, alpha = .1) +
  geom_line(data = prod_preds, 
            aes(y = pred, col = percentile, group = percentile))

  if (compare_newest_studies) {
    combined_production_plot <- combined_production_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "#249D00", data=both_data %>% filter(source == "webcdi" & study_group != newest_studies), aes(x = age, y = (production/n))) +
    geom_jitter(width = .6, size = 1, alpha = .6, colour = "red", data=both_data %>% filter(source == "webcdi" & study_group == newest_studies), aes(x = age, y =  (production/n)))
  } else{
    combined_production_plot <- combined_production_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "red", data=both_data %>% filter(source == "webcdi"), aes(x = age, y = (production/n)))
  }

  combined_production_plot <- combined_production_plot + scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 30, 4),
                     limits = c(8, 30),
                     name = "Age (months)") +
  ylab("Production Vocabulary\n(proportion of total words)") +
  scale_y_continuous(limits = c(0,1), labels = scales::percent) +
  theme(legend.position = "bottom")

  print(combined_production_plot)

```

Binned report of the % of words on the test reported as produced. Not a ranking.

```{r}

if (compare_newest_studies) {
  both_data$source[both_data$study_group == newest_studies] <- "webcdi-newest"
  both_data$source[both_data$study_group != newest_studies & both_data$source == "webcdi"] <- "webcdi-older"
}
binned_data <- both_data %>% 
  group_by(id, age, form, source, study_group) %>% 
  summarise(prop_prod = mean(production/n))

binned_data$`% of Words Produced`[binned_data$prop_prod < 0.25] <- "0-25%"
binned_data$`% of Words Produced`[binned_data$prop_prod >= 0.25 & binned_data$prop_prod < 0.50] <- "25-50%"
binned_data$`% of Words Produced`[binned_data$prop_prod >= 0.50 & binned_data$prop_prod < 0.75] <- "50-75%"
binned_data$`% of Words Produced`[binned_data$prop_prod >= 0.75] <- "75-100%"

ggplot(binned_data, aes(age, fill=`% of Words Produced`)) + 
  geom_bar(position = "fill", width=0.9) + 
  scale_y_continuous(labels = scales::percent) + 
  facet_wrap(~source) + 
  labs(y = "Production Vocabulary\n(% of total words)",
       x="Age (months)", fill = "") + 
  theme(legend.position = "bottom")
```
```{r}
binned_data_coarse <- both_data %>% 
  mutate(age = cut(age, seq(7,32,5))) %>%
  group_by(id, age, form, source, study_group) %>% 
  summarise(prop_prod = mean(production/n), 
            pctile = cut(prop_prod, seq(0, 1, .25)))

ggplot(binned_data_coarse, aes(age, fill=pctile)) + 
  geom_bar(position = "fill") + 
  scale_y_continuous(labels = scales::percent) + 
  facet_wrap(~source) + 
  labs(y = "Production Vocabulary\n(% of total words)",
       x="Age (months)", fill = "") + 
  theme(legend.position = "bottom", 
         axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5))
```



Percentile ranking based on original Wordbank production data. Wordbank graph included as a sanity check (each group should be around 25% for Wordbank data)

```{r}
taus <- seq(0.01,0.99, 0.01)

prod_models_perc <- prod_data %>%
  mutate(mean = jitter(mean, amount=0, factor = 0.3)) %>%
  split(.$language) %>%
  purrr::map(fit_gcrq) 

prod_preds_perc <- prod_data %>%
  group_by(language, age) %>%
  summarise(n = n()) %>%
  data.frame() %>%
  split(.$language) %>%
  map_df(function(x) pred_gcrq(x, prod_models_perc)) %>%
  mutate(percentile = as.numeric(percentile))

prop_prod <- both_data %>% 
  group_by(age) %>% 
  mutate(prop_production = production/n, quantile = NA)  %>%
  ungroup()

look_up_percentile <- function(x, perc) {
  if (x$production > 0) {
    x$quantile <- max(filter(perc, 
                           age == x$age, 
                           pred < x$prop_production)$percentile)
  } else {
    x$quantile < 0
  }
  
  return(x)
}

prop_prod <-  prop_prod %>%
  split(.$id) %>%
  map_df(function(x) look_up_percentile(x, prod_preds))


```


```{r}
prop_prod$bin_quantile <- as.character(cut(prop_prod$quantile, 
                                           seq(0,100, 25), 
                                           labels = c("1-25th","26-50th",
                                                      "51-75th","76-100th")))
prop_prod$bin_quantile[prop_prod$production == 0] <- "Did not produce"

webcdi_prop_prod <- prop_prod %>% filter(grepl('webcdi', source))
wordbank_prop_prod <- prop_prod %>% filter(source == "wordbank")

prop_prod_perc <- prop_prod %>% 
  group_by(source,bin_quantile) %>% 
  summarise(n=n()) %>% 
  group_by(source) %>% 
  mutate(perc=n/sum(n))

```

```{r}
ggplot(prop_prod_perc, 
       aes(x = factor(bin_quantile), y= perc, 
           fill=factor(bin_quantile))) + 
  facet_wrap(~source) + 
  geom_bar(stat="identity") + 
  scale_y_continuous(breaks = seq(0,1,0.25), 
                     labels = scales::percent) + 
  labs(x = "", fill="", y="% of Population", 
       title = "Production Percentile Ranking") + 
  theme(legend.position = "bottom", 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
```


```{r}
ggplot(prop_prod, aes(age, fill=factor(bin_quantile))) + 
  geom_bar(position = "fill", width=0.9) + 
  facet_wrap(~source) + 
  scale_y_continuous(breaks = seq(0,1,0.25), 
                     labels = scales::percent) + 
  labs(fill = "", y = "% of Population", x = "Age (months)", 
       title = "Production Percentile Ranking by Age") + 
  theme(legend.position = "bottom")
```

```{r}
webcdi_ranking_study_age <- ggplot(webcdi_prop_prod, aes(age, fill=factor(bin_quantile))) + geom_bar(position = "fill", width=0.9) + facet_wrap(~study_group) + scale_y_continuous(breaks = seq(0,1,0.25), labels = scales::percent) + labs(title = "Production Percentile Ranking", y = "Proportion of Population", x = "Age (months)", fill="") + theme(legend.position = "bottom")

print(webcdi_ranking_study_age)

wordbank_ranking_study_age <- ggplot(wordbank_prop_prod, aes(age, fill=factor(bin_quantile))) + geom_bar(position = "fill", width=0.9) + facet_wrap(~study_group) + scale_y_continuous(breaks = seq(0,1,0.25), labels = scales::percent) + labs(title = "Production Percentile Ranking", x="Age (months)", y="Proportion of Population", fill = "") + theme(legend.position = "bottom")

print(wordbank_ranking_study_age)

taus <-  c(0.1, 0.25, 0.5, 0.75, 0.9)

```


Maternal education differenes in vocab norms

```{r}
ses_data <- both_data %>% filter(!is.na(mom_ed))

ses_means <- ses_data %>%
  group_by(source, mom_ed, age) %>% 
  mutate(mean_production = production/n) %>%
  summarise(median = median(mean_production), n = n())

prop_ses_perc <- ses_data %>% 
  group_by(source,mom_ed) %>% 
  summarise(n=n()) %>% 
  group_by(source) %>% 
  mutate(perc=n/sum(n))

ses_composition <- ggplot(prop_ses_perc, aes(x = factor(mom_ed), y= perc, fill=factor(mom_ed))) + facet_wrap(~source) + geom_bar(stat="identity")+ scale_y_continuous(breaks = seq(0,1,0.25), labels = scales::percent) + labs(x = "", fill="", y="% of Population") + theme(legend.position = "bottom", axis.text.x = element_blank(), axis.ticks.x = element_blank())

print(ses_composition)

ses_models <- ses_data %>%
  split(.$source) %>%
  purrr::map(fit_ses) 

ses_preds <- expand.grid(source = unique(ses_means$source), 
                         age = min(ses_means$age):max(ses_means$age), 
                         mom_ed = unique(ses_means$mom_ed)) %>%
  split(.$source) %>%
  map_df(pred_ses_source)

ses_plot <- ggplot(ses_means,
       aes(x = age, y = median, colour = mom_ed, label = mom_ed)) +
  facet_wrap(~source) +
  geom_point(aes(size = n), alpha=.2) +
  geom_line(data = ses_preds, aes(y = pred)) + 
  scale_colour_solarized(name="Maternal Education") +
  scale_x_continuous(breaks = seq(min(ses_means$age), 
                                  max(ses_means$age), 4),
                     limits = c(min(ses_means$age), max(ses_means$age)),
                     name = "Age (months)") +
  labs(title = "Maternal Education Differences\nAcross Data and Age", y = "Median Productive Vocabulary\n(proportion of total words)") +
  theme(legend.title=element_blank()) +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")
print(ses_plot)

```

Sex differences in vocab norms

```{r}
sex_data <- both_data %>% filter(sex %in% c("Male","Female")) %>% mutate(mean_production = production/n)

prop_sex_perc <- sex_data %>% 
  group_by(source,sex) %>% 
  summarise(n=n()) %>% 
  group_by(source) %>% 
  mutate(perc=n/sum(n))

sex_composition <- ggplot(prop_sex_perc, aes(x = factor(sex), y= perc, fill=factor(sex))) + facet_wrap(~source) + geom_bar(stat="identity")+ scale_y_continuous(breaks = seq(0,1,0.25), labels = scales::percent) + labs(x = "", fill="", y="% of Population") + theme(legend.position = "bottom", axis.text.x = element_blank(), axis.ticks.x = element_blank())

print(sex_composition)

sex_means <- sex_data %>% group_by(source, sex, age) %>% summarise(production = median(mean_production))

sex_models <- sex_data %>%
  split(.$source) %>%
  purrr::map(fit_sex) 

sex_preds <- expand.grid(source = unique(sex_means$source), 
                         age = min(sex_means$age):max(sex_means$age), 
                         sex = unique(sex_means$sex)) %>%
  split(.$source) %>%
  map_df(pred_sex_source)

sex_plot <- ggplot(sex_means,
       aes(x = age, y = production, colour = sex, label = sex)) +
  facet_wrap(~source) +
  geom_point(alpha=.2) +
  geom_line(data = sex_preds, aes(y = pred)) + 
  scale_colour_solarized(name="Sex") +
  scale_x_continuous(breaks = seq(min(sex_means$age), 
                                  max(sex_means$age), 4),
                     limits = c(min(sex_means$age), max(sex_means$age)),
                     name = "Age (months)") +
  labs(title = "Sex Differences\nAcross Data and Age", y = "Median Productive Vocabulary\n(proportion of total words)") +
  theme(legend.title=element_blank()) +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(sex_plot)
```


```{r}
data(zipcode)

zip_data <- slim_webcdi_data %>%
  filter(analysis) %>%
  group_by(study_name, zip_code) %>%
  summarise(n = n()) %>%
  mutate(zip_code = substr(zip_code,1,3))

zip_prefix <- zipcode %>%
  mutate(zip_prefix = substr(zip,1,3)) %>%
  group_by(zip_prefix) %>%
  summarise(latitude = mean(latitude, na.rm=T),
            longitude = mean(longitude, na.rm = T))

zip_data %<>%
  left_join(zip_prefix, by = c("zip_code" = "zip_prefix"))

us<-map_data('state')

map_plot <- ggplot(zip_data,aes(longitude,latitude)) +
  geom_polygon(data=us,aes(x=long,y=lat,group=group),color='gray',fill=NA,alpha=.35)+
  geom_point(aes(size = n, colour = study_name),alpha=.25) +
  theme_mikabr()+
  xlim(-125,-65)+ylim(20,50)
```



```{r include=FALSE}
object_names <- ls()
for (i in 1:length(object_names)) {
  if(is.ggplot(get(object_names[i]))) {
    ggsave(plot = get(object_names[i]), filename = paste0("graphs/",object_names[i],".png"), width = 16, height = 9, units = "cm")
  }
}

```

