---
title: Comparison of Web-CDI Data Collected from Amazon Mechanical Turk against Data
  from Aggregated CDI studies
author: ''
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
  html_notebook:
    code_folding: hide
    highlight: tango
    theme: spacelab
    toc: yes
  pdf_document:
    toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```


Load up necessary packages and scripts for accessing both the Wordbank MySQL database and the Web-CDI database.

```{r}
library(tidyverse)
library(quantregGrowth)
library(wordbankr)
library(langcog)
library(stringr)
library(RPostgreSQL)
library(lubridate)
library(robustbase)
library(forcats)
theme_set(theme_mikabr(base_size = 18))

source("access-webcdi.R")
source("predictQR_fixed.R")
mode <- "remote"
compare_newest_studies <- F
newest_studies <- "MTurk-5"
taus <- seq(0.01,0.99, 0.01)
# taus <-  c(0.1, 0.25, 0.5, 0.75, 0.9)



```

Word categories classified into nouns and verbs
```{r}
nouns <- c("animals", "vehicles","toys","food_drink","clothing","body_parts","furniture_rooms","household","outside","people")
verbs <- c("action_words","helping_verbs")
```


Collect data from wordbank.
```{r}
num_words <- get_item_data() %>%
  filter(type == "word") %>%
  group_by(language, form) %>%
  summarise(n = n())

vocab_data <- get_administration_data() %>%
  select(data_id, language, form, age, sex, 
         mom_ed, birth_order, production, comprehension, source_name) %>% 
  left_join(num_words) %>%
  mutate(no_production = n - production)

min_age <- min(vocab_data$age)
max_age <- max(vocab_data$age)
```

Functions for modelling quantiles for Wordbank data.
```{r}

fit_gcrq <- function(x) {
  mod <- try(gcrq(formula = mean ~ ps(age, monotone = 1, 
                                      lambda = 1000), 
                  tau = taus, data = x))

  if(inherits(mod, "try-error"))
  {
    return(NA)
  }

  return(mod)
}

pred_gcrq <- function(x, mods) {
  mod <- mods[[x$language[1]]]

  if (is.na(mod[1])) {
    return(expand.grid(age = x$age, 
                       language = x$language[1], 
                       percentile = as.character(taus*100), 
                       pred = NA))
  } else {
    preds <- predictQR_fixed(mod, 
                             newdata = x) %>%
      data.frame %>%
      mutate(age = x$age, 
             language = x$language) %>%
      gather(percentile, pred, starts_with("X")) %>%
      mutate(percentile = as.character(as.numeric(str_replace(percentile, 
                                                              "X", "")) 
                                       * 100))
    return(preds)
  }
}

fit_sex <- function(x) {
  robustbase::glmrob(cbind(production, no_production) ~ age * sex - sex,
                     family = "binomial",
                     data = x)
}

pred_sex <- function(x, model) {
  x$pred <- predict(model[[x$language[1]]], 
                    newdata = x, type = "response")
  return(x)
}

fit_ses <- function(x) {
  robustbase::glmrob(cbind(production, no_production) ~ 
                       age * mom_ed  - mom_ed,
                     family = "binomial",
                     data = x)
}

pred_ses <- function(x, model) {
  x$pred <- predict(model[[x$language[1]]], 
                    newdata = x, type = "response")
  return(x)
}

```

Grab English WG comprehension data from Wordbank and plot alone with model
```{r}
comp_data <- vocab_data %>%
  filter(form == "WG" &  language == "English") %>%
  mutate(mean = comprehension / n)

comp_models <- comp_data %>%
  split(.$language) %>%
  map(fit_gcrq) 

comp_preds <- comp_data %>%
  group_by(language, age) %>%
  summarise(n = n()) %>%
  data.frame() %>%
  split(.$language) %>%
  map_df(function(x) pred_gcrq(x, comp_models)) 

wordbank_comprehension_plot <- ggplot(comp_data,
       aes(x = age, y = mean)) +
  facet_wrap(~language) +
  geom_jitter(width = .4, size = 1, alpha = .1) +
  geom_line(data = comp_preds, 
            aes(y = pred, col = percentile, group = percentile)) + 
  scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 18, 4),
                     limits = c(8, 18),
                     name = "Age (months)") +
  ylab("Comprehension Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(wordbank_comprehension_plot)

```

Grab production data from English WG and WS for Wordbank and plot data alone with model

```{r}
prod_data <- vocab_data %>%
  filter(language == "English") %>%
  mutate(mean = production / n)

prod_models <- prod_data %>%
  split(.$language) %>%
  map(fit_gcrq) 

prod_preds <- prod_data %>%
  group_by(language, age) %>%
  summarise(n = n()) %>%
  data.frame() %>%
  split(.$language) %>%
  map_df(function(x) pred_gcrq(x, prod_models)) 

wordbank_production_plot <- ggplot(prod_data,
       aes(x = age, y = mean)) +
  facet_wrap(~language) +
  geom_jitter(width = .4, size = 1, alpha = .1) +
  geom_line(data = prod_preds, 
            aes(y = pred, col = percentile, group = percentile)) + 
  scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 36, 4),
                     limits = c(8, 36),
                     name = "Age (months)") +
  ylab("Production Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(wordbank_production_plot)
```

Access Web-CDI database and find data from the studies of interest (labeled 'MTurk').
Grab the related CDI items. There are one set each for the two instruments.

```{r}

webcdi <- connect_to_webcdi(mode=mode)
study_info <- get_common_table(webcdi, "researcher_UI_study") %>% as.data.frame() %>% filter(grepl('MTurk', name)) %>% rename(study_id = id, instrument = instrument_id)
instruments <- unique(study_info$instrument)
study_items <- list()

for (i in 1:length(instruments)){
  temp <- get_common_table(webcdi, paste("cdi_forms", tolower(instruments[i]), sep="_")) %>% as.data.frame() %>% rename(item_ID = itemID)
  study_items[[i]] <- temp
  study_items[[i]]$instrument <- instruments[i]
}

cdi_items <- bind_rows(study_items) %>% filter(!grepl('example', item_ID))

```

Grab by-child data (administration details, demographic information, and given answers)
```{r}

admin_info <- get_common_table(webcdi, "researcher_UI_administration") %>% as.data.frame() %>% filter(study_id %in% study_info$study_id & completed) %>% rename(administration_id = id)

background_info <- get_common_table(webcdi, "cdi_forms_backgroundinfo") %>% as.data.frame() %>% filter(administration_id %in% admin_info$administration_id) %>% filter(birth_weight >= 5.5)

cdi_answers <- get_common_table(webcdi, "researcher_UI_administration_data") %>% as.data.frame() %>% filter(administration_id %in% admin_info$administration_id) %>% select(-id)

```

Merge Web-CDI tables.
Calculate proportions of words understood and words produced.
```{r}

combined_data <- left_join(background_info, admin_info, by = "administration_id") %>% left_join(., study_info, by = "study_id") %>% left_join(., cdi_items, by = c("instrument")) %>% left_join(., cdi_answers, by = c("administration_id", "item_ID")) %>% filter( grepl('WG', instrument) & (age >= 8 & age <= 18) | grepl('WS', instrument) & (age >= 16 & age <= 30))

combined_words <- combined_data %>% filter(item_type == "word")
combined_words$value[is.na(combined_words$value)] <- "neither"

combined_words$word_type[combined_words$category %in% nouns] <- "nouns"
combined_words$word_type[combined_words$category %in% verbs] <- "verbs"

if (compare_newest_studies) {
  combined_words$newest <- FALSE
  combined_words$newest[combined_words$study_group == newest_studies] <- TRUE
  
  prop_measures <- combined_words %>% group_by(id, age, newest) %>% summarise(comprehension = sum(value == "understands" | value == "produces")/n(), production = sum(value == "produces")/n())
  
  prop_measures_old <- prop_measures %>% filter(!newest)
  prop_measures_new <- prop_measures %>% filter(newest)
} else {
    prop_measures <- combined_words %>% group_by(id, age) %>% summarise(comprehension = sum(value == "understands" | value == "produces")/n(), production = sum(value == "produces")/n())
}

```

Plot Wordbank data with Web-CDI data (in red) along with the original model lines.

```{r}

combined_comprehension_plot <- ggplot(comp_data,
       aes(x = age, y = mean)) +
  facet_wrap(~language) +
  geom_jitter(width = .4, size = 1, alpha = .1) +
  geom_line(data = comp_preds, 
            aes(y = pred, col = percentile, group = percentile))

  if (compare_newest_studies) {
    combined_comprehension_plot <- combined_comprehension_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "#249D00", data=prop_measures_old, aes(x = age, y = comprehension)) +
    geom_jitter(width = .6, size = 1, alpha = .6, colour = "red", data=prop_measures_new, aes(x = age, y = comprehension))
  } else{
    combined_comprehension_plot <- combined_comprehension_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "red", data=prop_measures, aes(x = age, y = comprehension))
  }
  
  combined_comprehension_plot <- combined_comprehension_plot + scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 18, 4),
                     limits = c(8, 18),
                     name = "Age (months)") +
  ylab("Comprehension Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

  print(combined_comprehension_plot)


combined_production_plot <- ggplot(prod_data,
       aes(x = age, y = mean)) +
  facet_wrap(~language) +
  geom_jitter(width = .4, size = 1, alpha = .1) + 
  geom_line(data = prod_preds, 
            aes(y = pred, col = percentile, group = percentile))

  if (compare_newest_studies) {
    combined_production_plot <- combined_production_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "#249D00", data=prop_measures_old, aes(x = age, y = production)) +
  geom_jitter(width = .4, size = 1, alpha = .6, colour = "red", data=prop_measures_new, aes(x = age, y = production))
    
  } else {
    combined_production_plot <- combined_production_plot + geom_jitter(width = .4, size = 1, alpha = .6, colour = "red", data=prop_measures, aes(x = age, y = production))
  }

  combined_production_plot <- combined_production_plot + scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 30, 4),
                     limits = c(8, 30),
                     name = "Age (months)") +
  ylab("Production Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

  print(combined_production_plot)

```

Further splitting data by word_type

```{r}
type_measures <- combined_words %>% group_by(id, age, word_type) %>% filter(!is.na(word_type)) %>% summarise(comprehension = sum(value == "understands" | value == "produces")/n(), production = sum(value == "produces")/n())

group_type_measures <- type_measures %>% group_by(age, word_type) %>% summarise(comprehension = mean(comprehension), production = mean(production))

type_comprehension_plot <- ggplot(comp_data,
       aes(x = age, y = mean)) +
  facet_wrap(~language) +
  geom_jitter(width = .4, size = 1, alpha = .1) +
  geom_line(data = comp_preds, 
            aes(y = pred, col = percentile, group = percentile)) + 
  geom_jitter(width = .4, size = 1, alpha = .6, data=type_measures, aes(x = age, y = comprehension, colour = word_type)) +
  scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 18, 4),
                     limits = c(8, 18),
                     name = "Age (months)") +
  ylab("Comprehension Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(type_comprehension_plot)


type_production_plot <- ggplot(prod_data,
       aes(x = age, y = mean)) +
  facet_wrap(~language) +
  geom_jitter(width = .4, size = 1, alpha = .1) + 
  geom_line(data = prod_preds, 
            aes(y = pred, col = percentile, group = percentile)) + 
  geom_jitter(width = .4, size = 1, alpha = .6, data=type_measures, aes(x = age, y = production, colour = word_type)) +
  scale_colour_solarized(name="Percentile") +
  scale_x_continuous(breaks = seq(8, 30, 4),
                     limits = c(8, 30),
                     name = "Age (months)") +
  ylab("Production Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(type_production_plot)
```

Can look at the start and end times for studies done 1/11/17 morning PDT time and after.

```{r}
times <- as.data.frame(matrix(nrow = nrow(admin_info),ncol=2))
names(times) <- c("start_time","end_time")

times$start_time <- admin_info$created_date
times$end_time <- admin_info$last_modified

times <- with_tz(times, "UTC") %>% filter(start_time > as.POSIXlt("2017-01-11 09:00:00 PDT"))

times$completion_time <- times$end_time - times$start_time
times$num_range <- seq(1,nrow(times)*2,2)

ggplot(times, aes(xmin = start_time, xmax = end_time, ymin = num_range, ymax = num_range + 1, fill = factor(num_range))) + geom_rect() + theme(legend.position = "none")
```


Sex differences in English Wordbank Data
```{r}

wordbank_sex_data <- vocab_data %>%
  filter(!is.na(sex), language == "English") 

wordbank_sex_means <- wordbank_sex_data %>%
  group_by(language, sex, age) %>%
  summarise(median = median(production/n))

wordbank_sex_models <- wordbank_sex_data %>%
  split(.$language) %>%
  map(fit_sex) 

wordbank_sex_preds <- expand.grid(language = unique(wordbank_sex_means$language), 
                         age = min_age:max_age, 
                         sex = unique(wordbank_sex_means$sex)) %>%
  split(.$language) %>%
  map_df(pred_sex, model = wordbank_sex_models)

wordbank_sex_plot <- ggplot(wordbank_sex_means,
       aes(x = age, y = median, colour = sex, label = sex)) +
  facet_wrap(~language) +
  geom_point(alpha=.2) +
  geom_line(data = wordbank_sex_preds, aes(y = pred)) + 
  scale_colour_solarized(name="Sex") +
  scale_x_continuous(breaks = seq(min(wordbank_sex_means$age), 
                                  max(wordbank_sex_means$age), 4),
                     limits = c(min(wordbank_sex_means$age), max(wordbank_sex_means$age)),
                     name = "Age (months)") +
  ylab("Median Productive Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(wordbank_sex_plot)

```

Sex differences in Web-CDI Data

```{r}
webcdi_sex_data <- combined_words %>% filter(sex %in% c("M","F")) %>% group_by(id, sex, age) %>% summarise(production = sum(value == "produces"), no_production = sum(value != "produces"), mean_production = sum(value == "produces")/n(), language = "English")

webcdi_sex_data$sex[webcdi_sex_data$sex == "F"] <- "Female"
webcdi_sex_data$sex[webcdi_sex_data$sex == "M"] <- "Male"

webcdi_sex_means <- webcdi_sex_data %>% group_by(sex, age, language) %>% summarise(production = median(mean_production))

webcdi_sex_models <- webcdi_sex_data %>%
  split(.$language) %>%
  map(fit_sex) 

webcdi_sex_preds <- expand.grid(language = unique(webcdi_sex_means$language), 
                         age = min(webcdi_sex_means$age):max(webcdi_sex_means$age), 
                         sex = unique(webcdi_sex_means$sex)) %>%
  split(.$language) %>%
  map_df(pred_sex, model = webcdi_sex_models)

webcdi_sex_plot <- ggplot(webcdi_sex_means,
       aes(x = age, y = production, colour = sex, label = sex)) +
  facet_wrap(~language) +
  geom_point(alpha=.2) +
  geom_line(data = webcdi_sex_preds, aes(y = pred)) + 
  scale_colour_solarized(name="Sex") +
  scale_x_continuous(breaks = seq(min(webcdi_sex_means$age), 
                                  max(webcdi_sex_means$age), 4),
                     limits = c(min(webcdi_sex_means$age), max(webcdi_sex_means$age)),
                     name = "Age (months)") +
  ylab("Median Productive Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(webcdi_sex_plot)
```

Looking at traditional Wordbank Data for Maternal Education Differences

```{r}
wordbank_ses_data <- vocab_data %>%
  filter(!is.na(mom_ed), language == "English") %>%
  mutate(mom_ed = fct_collapse(mom_ed, 
                               `Below Secondary` = c("None","Primary",
                                                     "Some Secondary"),
                               `Secondary` = c("Secondary", "Some College"),
                               `College and Above` = c("College", 
                                                       "Some Graduate", 
                                                       "Graduate")))

wordbank_ses_means <- wordbank_ses_data %>%
  group_by(language, mom_ed, age) %>%
  summarise(median = median(production/n))

wordbank_ses_models <- wordbank_ses_data %>%
  split(.$language) %>%
  map(fit_ses) 

wordbank_ses_preds <- expand.grid(language = unique(wordbank_ses_means$language), 
                         age = min_age:max_age, 
                         mom_ed = unique(wordbank_ses_means$mom_ed)) %>%
  split(.$language) %>%
  map_df(pred_ses, model = wordbank_ses_models)

wordbank_ses_plot <- ggplot(wordbank_ses_means,
       aes(x = age, y = median, colour = mom_ed, label = mom_ed)) +
  facet_wrap(~language) +
  geom_point(alpha=.2) +
  geom_line(data = wordbank_ses_preds, aes(y = pred)) + 
  scale_colour_solarized(name="Maternal Education") +
  scale_x_continuous(breaks = seq(min(wordbank_ses_means$age), 
                                  max(wordbank_ses_means$age), 4),
                     limits = c(min(wordbank_ses_means$age), max(wordbank_ses_means$age)),
                     name = "Age (months)") +
  ylab("Median Productive Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(wordbank_ses_plot)

```

Comparison of Web-CDI SES Data.

```{r}

webcdi_ses_data <- combined_words %>%
  filter(!is.na(mother_education)) %>% group_by(id, mother_education, age) %>% summarise(production = sum(value == "produces"), no_production = sum(value != "produces"), mean_production = sum(value == "produces")/n(), language = "English") %>%
  rename(mom_ed = mother_education)

webcdi_ses_data$mom_ed[webcdi_ses_data$mom_ed %in% 0:9] <- "Below Secondary"
webcdi_ses_data$mom_ed[webcdi_ses_data$mom_ed %in% 10:13] <- "Secondary"
webcdi_ses_data$mom_ed[webcdi_ses_data$mom_ed %in% 14:25] <- "College and Above"

#currently not enough subjects with mom_ed = "below secondary", skewing results
webcdi_ses_data <- webcdi_ses_data %>% filter(mom_ed != "Below Secondary")

webcdi_ses_means <- webcdi_ses_data %>%
  group_by(language, mom_ed, age) %>%
  summarise(median = median(mean_production))

webcdi_ses_models <- webcdi_ses_data %>%
  split(.$language) %>%
  map(fit_ses) 

webcdi_ses_preds <- expand.grid(language = unique(webcdi_ses_means$language), 
                         age = min(webcdi_ses_means$age):max(webcdi_ses_means$age), 
                         mom_ed = unique(webcdi_ses_means$mom_ed)) %>%
  split(.$language) %>%
  map_df(pred_ses, model = webcdi_ses_models)

webcdi_ses_plot <- ggplot(webcdi_ses_means,
       aes(x = age, y = median, colour = mom_ed, label = mom_ed)) +
  facet_wrap(~language) +
  geom_point(alpha=.2) +
  geom_line(data = webcdi_ses_preds, aes(y = pred)) + 
  scale_colour_solarized(name="Maternal Education") +
  scale_x_continuous(breaks = seq(min(webcdi_ses_means$age), 
                                  max(webcdi_ses_means$age), 4),
                     limits = c(min(webcdi_ses_means$age), max(webcdi_ses_means$age)),
                     name = "Age (months)") +
  ylab("Median Productive Vocabulary\n(proportion of total words)") +
  ylim(c(0, 1)) + 
  theme(legend.position = "bottom")

print(webcdi_ses_plot)

```



```{r}

slim_wordbank_data <- vocab_data %>% filter(language == "English") %>% rename(id = data_id, study_group = source_name) %>% select(id, form, age, sex, production, comprehension, n, study_group) %>% mutate(data = "wordbank")

slim_webcdi_data <- combined_words %>% group_by(id, instrument, age, sex, study_group) %>% summarise(comprehension = sum(value == "understands" | value == "produces"), production = sum(value == "produces"), n = n(), data = "webcdi")

slim_webcdi_data$form[grepl('WG', slim_webcdi_data$instrument)] <- "WG"
slim_webcdi_data$form[grepl('WS', slim_webcdi_data$instrument)] <- "WS"
slim_webcdi_data$instrument <- NULL

a <- list(slim_webcdi_data, slim_wordbank_data)

for (i in 1:length((a))) {
  temp <- a[[i]]
  temp <- temp[,c("id","form","age","sex","production","comprehension","n","data", "study_group")]
  a[[i]] <- temp
  
}

both_data <- bind_rows(a)

binned_data <- both_data %>% group_by(id, age, form, data) %>% summarise(prop_prod = mean(production/n)) 

binned_data$`% of Words Produced`[binned_data$prop_prod < 0.25] <- "0-25%"
binned_data$`% of Words Produced`[binned_data$prop_prod >= 0.25 & binned_data$prop_prod < 0.50] <- "25-50%"
binned_data$`% of Words Produced`[binned_data$prop_prod >= 0.50 & binned_data$prop_prod < 0.75] <- "50-75%"
binned_data$`% of Words Produced`[binned_data$prop_prod >= 0.75] <- "75-100%"

ggplot(binned_data, aes(age, fill=`% of Words Produced`)) + geom_bar(position = "fill", width=0.9) + facet_wrap(~data) + ylab("Production Vocabulary\n(proportion of total words)") + theme(legend.position = "bottom")

```


Match Web-CDI Data based on Wordbank quantiles
```{r}

webcdi_prop_prod <- slim_webcdi_data %>% filter(study_group %in% c("MTurk-3","MTurk-4","MTurk-5")) %>% group_by(age ) %>% mutate(prop_production = production/n, quantile = NA)


for (i in 1:nrow(webcdi_prop_prod)) {
  current_age <- webcdi_prop_prod$age[i]
  current_prod <- webcdi_prop_prod$prop_production[i]
  
  ranges_at_age <- prod_preds %>% filter(age == current_age, pred < current_prod)
  
  webcdi_prop_prod$quantile[i] <- max(max(as.numeric(as.character(ranges_at_age$percentile))),1)
  
  
}

webcdi_prop_prod$quantile[webcdi_prop_prod$production == 0] <- 0
webcdi_prop_prod$bin_quantile <- as.character(cut(webcdi_prop_prod$quantile, seq(0,100, 25), labels = c("1-25th","26-50th","51-75th","76-100th")))
webcdi_prop_prod$bin_quantile[webcdi_prop_prod$production == 0] <- "Did not produce"

ggplot(webcdi_prop_prod, aes(factor(bin_quantile), fill=factor(bin_quantile))) + geom_bar() + scale_y_continuous(breaks = seq(0,100,25)) + labs(fill = "Production Percentile Ranking\nAgainst Wordbank Data") + theme(legend.position = "bottom")

ggplot(webcdi_prop_prod, aes(age, fill=factor(bin_quantile))) + geom_bar(position = "fill", width=0.9) + facet_wrap(~study_group) + scale_y_continuous(breaks = seq(0,1,0.25), labels = scales::percent) + ylab("Proportion of Population") + labs(fill = "Production Percentile Ranking\nAgainst Wordbank Data") + theme(legend.position = "bottom")

```


```{r}

wordbank_prop_prod <- slim_wordbank_data %>% mutate(prop_production = production/n, quantile = NA)

for (i in 1:nrow(wordbank_prop_prod)) {
  current_age <- wordbank_prop_prod$age[i]
  current_prod <- wordbank_prop_prod$prop_production[i]
  
  ranges_at_age <- prod_preds %>% filter(age == current_age, pred < current_prod)
  
  wordbank_prop_prod$quantile[i] <- max(max(as.numeric(as.character(ranges_at_age$percentile))),1)
  
}

wordbank_prop_prod$quantile[wordbank_prop_prod$production == 0] <- 0
wordbank_prop_prod$bin_quantile <- as.character(cut(wordbank_prop_prod$quantile, seq(0,100, 25), labels = c("1-25th","26-50th","51-75th","76-100th")))
wordbank_prop_prod$bin_quantile[wordbank_prop_prod$production == 0] <- "Did not produce"

ggplot(wordbank_prop_prod, aes(factor(bin_quantile), fill=factor(bin_quantile))) + geom_bar()  + scale_y_continuous(breaks = seq(0,2000,500)) + labs(fill = "Production Percentile Ranking\nAgainst Wordbank Data") + theme(legend.position = "bottom")

ggplot(wordbank_prop_prod, aes(age, fill=factor(bin_quantile))) + geom_bar(position = "fill", width=0.9) + facet_wrap(~study_group) + scale_y_continuous(breaks = seq(0,1,0.25), labels = scales::percent) + ylab("Proportion of Population") + labs(fill = "Production Percentile Ranking") + theme(legend.position = "bottom")

```

